---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# psychtopics

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
<!-- badges: end -->


## Running the app  

There are two ways to run the app.  

### First way  

Install the app from github and run!  

```{r eval=FALSE}

## install from github
devtools::install_github("shahreyar-abeer/upwork_andre_psychtopics")

## if the installation is successful, the app should run with this command!
psychtopics::run_app()

```

### Second way  

1. Open RStudio > File > New_Project > Version Control > Git  
2. Paste this link in the dialog box https://github.com/shahreyar-abeer/upwork_andre_psychtopics  
3. Once the project is created, navigate to `dev/run_dev.R`  
4. Select everything in the script and run `(Ctrl + Enter)`  
5. The app should be up and running!  

Let me know if you face any issues.